Plots

### 2025-02-25 src/plots.Rmd
Add pccc age plot

## Age Case Count

Count the number and percentage of cases for each age group.

@@

# Count cases per cod
df <- df %>%
    left_join( # count cases and add as column
        df %>%
            group_by(age, physician_cghr10) %>%
            count(name = "physician_cghr10_n") %>%
            group_by(age) %>%
            mutate(
                physician_cghr10_perc = (physician_cghr10_n / sum(physician_cghr10_n)) * 100
            ),
        by = c("age", "physician_cghr10")
    )
df %>% select(rowid, age, physician_cghr10, physician_cghr10_n)
```

@@

@@

```{r}
plot_perf(
    df_long,
    calc_pccc,
    group = "age_name",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death",
    text_mid_size = 2.5,
    text_mid_vjust = 3
)
```

@@

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("(a) Adult Records (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(b) Child Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(c) Neonatal Records (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )

>>>>

@@

# Count cases per cod
df <- df %>%
    left_join( # count cases and add as column
        df %>%
            group_by(age, physician_cghr10) %>%
            count(name = "physician_cghr10_n") %>%
            group_by(age) %>%
            mutate(
                physician_cghr10_perc = (physician_cghr10_n / sum(physician_cghr10_n)) * 100
            ),
        by = c("age", "physician_cghr10")
    )
df %>% select(rowid, age, physician_cghr10, physician_cghr10_n)

@@

# Calc perc of records for each age
perc_adult <- (n_adult / nrow(df)) * 100
perc_child <- (n_child / nrow(df)) * 100
perc_neo <- (n_neo / nrow(df)) * 100

@@

```{r}
plot_perf(
    df_long %>%
        mutate(
            age_label = case_when(
                age_name == "Adult"
                    ~ paste0(age_name, "\n12+ Years\n(n=", n_adult, ", ", round(perc_adult), "%)"),
                age_name == "Child"
                    ~ paste0(age_name, "\n28 Days to 11 Years\n(n=", n_child, ", ", round(perc_child), "%)"),
                age_name == "Neonate"
                    ~ paste0(age_name, "\n<28 Days\n(n=", n_neo, ", ", round(perc_neo), "%)"),
                .default = age_name
            )
        ),
    calc_pccc,
    group = "age_label",
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = paste0("Physician Agreed Records (n=", nrow(df), ")"),
    text_mid_size = 2.5,
    text_mid_vjust = 3
)
```

@@

# Plot perf for pccc
plot_perf(
    df_long %>% filter(age == "adult"),
    calc_pccc,
    group = "cod_name",
    title = paste0("(a) Adult, 12+ Years (n=", n_adult, ")"),
    x_title = "Partial Chance Corrected Concordance (PCCC)",
    y_title = "Cause of Death"
) /
    plot_perf(
        df_long %>% filter(age == "child"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(b) Child, 28 Days to 11 Years (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death"
    ) /
    plot_perf(
        df_long %>% filter(age == "neo"),
        calc_pccc,
        group = "cod_name",
        title = paste0("(c) Neonatal, <28 Days (n=", n_child, ")"),
        x_title = "Partial Chance Corrected Concordance (PCCC)",
        y_title = "Cause of Death",
        text_mid_vjust = 3
    ) +
    plot_layout(
        heights = c(2, 1, 1),
        axis_titles = "collect"
    )
